### 2019-05-22 4_implementation.tex
Remove resolved FIXMEs.
Update list of systems.
Fiddle with figure placement, labels, listing font size.
Only claim 15 systems so we don't have to quibble about MPI+CUDA not running on Cori.
Add Dask text.

We have implemented Task Bench in the 13 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. We describe the
systems, and any salient details of their Task Bench implementations,
below.

@@

% FIXME: Discuss load balancer

@@

% FIXME: bulk synchronous or point-to-point

@@

@@

% FIXME: keep this in sync with experiments

>>>>

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. We describe the
systems, and any salient details of their Task Bench implementations,
below.

@@

\subsection{Dask}

Dask is an implicitly parallel task-based programming system for large
scale data analytics with Python. Dask provides abstractions over
distributed NumPy arrays and Pandas dataframes, and also a lower-level
interface for launching tasks. We use the lower-level interface to
implement Task Bench.

@@

@@

\subsection{MPI+X}

% FIXME: TODO

@@
